Indirect elicitation as a necessary condition: followup

### 2020-12-08 colt-21/cvx-flats.tex
Adding COLT 2021 files

\title[Indirect elicitation necessary for consistent surrogates]{Indirect elicitation as a necessary condition for consistent surrogate losses}
\usepackage{times}

@@

%\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
\newcommand{\discuss}[1]{\mytodo{cyan!20!white}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

@@

Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
In both of these settings, a minimal requirement of a surrogate loss is \emph{consistency}, a precursor to excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.

Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension can increase the computational and sample complexity of learning.
We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.  I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.  Probably the biggest issue was in laying out the gap.  You often need to give more detail about what \emph{has} been done to say what hasn't.}

While meaningful bounds on the prediction dimension have recently begun to appear, both for discrete and continuous predictions~\cite{lambert2008eliciting,ramaswamy2016convex,ramaswamy2018consistent,frongillo2018elicitation}, these works have several drawbacks.
Consistency for discrete target losses is typically studied using calibration, which though powerful and undeniably useful, can be challenging to work with, and general results about calibration are sparse.
In the case of continuous predictions, results for \emph{convex} surrogates remain a major open problem~\cite{frongillo2018elicitation}.

Our results make two contributions toward closing this gap.
First, after introducing a general definition of consistency (\S~\ref{sec:consis-implies-indir}) which applies to all of the settings mentioned above, we show that indirect property elicitation is a necessary condition for consistency in all these settings (Theorem~\ref{thm:consistent-implies-indir-elic}).
As indirect elicitation is more tractable than calibration, and applies more generally, this observation suggests indirect elicitation as the better choice to study lower bounds on the prediction dimension of a consistent surrogate.
Second, we state a general lower bound on the prediction dimension of a consistent \emph{convex} surrogate (Theorem~\ref{thm:cvx-flats}).
Our result generalizes a calibration result of \citet{ramaswamy2016convex} to all of the above 
%\botodo{Again we mention the four settings, but we haven't said what they are. probably should either say it explicitly, or change this to something like ``all the above settings''} 
settings, yielding to our knowledge the most general such bound.
A caveat to these results is that, unlike \citet{ramaswamy2016convex}, we generally require surrogates to be ``minimizable'', i.e. functions that attain their global infimum.
Removing this requirement is a technically interesting and perhaps useful direction for future work.

%\botodo{modified this last paragraph a bit}\raft{added ``essentially'' again... such a great word, isn't it?}
While indirect elicitation is only a necessary condition, our bounds often recover or improve upon the state of the art.
For discrete predictions, for minimizable surrogates we recover (in Corollary \ref{cor:fsd-bound}) the feasible subspace dimension bounds of \citet{ramaswamy2016convex} and give tighter bounds in some cases.
Meanwhile, in the continuous prediction setting, essentially no bounds for convex surrogates were known~\citep{frongillo2018elicitation}, and our lower bounds match the best upper bounds.
For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.
%While indirect elicitation is only a necessary condition, our bounds recover or improve upon the state of the art:
%we achieve tighter bounds than the feasible subspace dimension approach for discrete predictions~\citep{ramaswamy2016convex}, yet recover their result (Corollary~\ref{cor:fsd-bound}), and no bounds for convex surrogates were known in the continuous prediction setting~\citep{frongillo2018elicitation}.
%Furthermore, in all of the examples we consider, our lower bounds match the best upper bounds.
%For these reasons, we advocate for indirect elicitation as a tractable and more general alternative to calibration when studying the consistency of surrogates.

%We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
%The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
%\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.

% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
% the existence of consistent convex surrogates in a given dimension $d$.
% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propagated}

@@

An important caveat to the above definitions is that, since $\Gamma = \prop{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\raft{Check me!}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessiet{I might suggest cutting this paragraph for the sake of space?}
\raft{Kept it and squoze elsewhere}

@@

If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the regret with respect to $\ell$, the two definitions are equivalent. % for the appropriate choice of $\propdis$.
% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Given a surrogate loss $L$, link $\psi$, and target loss $\ell$, set
	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
  $\mu(r,p) := R_\ell(r,p)$.
  Then
	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
  \btw{Note: don't actually need $\gamma$ nonempty here.}
\end{lemma}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
        \begin{align}
	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
	\end{align}
        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
\end{proof}

@@

We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
\raft{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.

>>>>

\usepackage{times}

@@

%\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mynote{orange!80!white}{BTW: #1}}
\newcommand{\discuss}[1]{\mynote{cyan!20!white}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\title[Indirect elicitation necessary for consistent surrogates]{Indirect elicitation as a necessary condition for consistent surrogate losses\jessie{Change this as we reframe??}}

@@

%supervised learning blah
Surrogate risk minimization is one of the most widespread techniques in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
Often, we desire surrogate losses to be \emph{consistent}, as this precedes deriving excess risk bounds and rates.
Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest:
the target risk should also be minimized, or the average deviation to the true conditional statistic function converges to 0.

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for these tasks.
Until recently, the dimensionality of such surrogate prediction space has typically scaled linearly with the number of outcomes unless sacrifices are made in terms of consistency.
This linear growth of prediction dimension in the number of outcomes leads to computationally expensive or intractable optimization problems, but it is unknown when it is possible to optimize a surrogate in a lower-dimensional prediction space for many tasks that have large outcome spaces.

However, for some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain loss~\citep{ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain loss that takes as input a prediction in an exponentially lower dimension than the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that reports are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This loss allows one to optimize this BEP loss that takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$.

%in a seemingly unrelated setting, finance problems blah blah.
In its own line of literature, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, estimate the desired statistic.
For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments, which yields an unbiased estimator of the variance.
However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
\jessie{Raf, helppp}

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
The two examples above are seemingly unrelated given how different the settings are; in the abstain problem, we have a finite prediction problem where we want to design a consistent convex surrogate for a given target loss.
In risk estimation, on the other hand, we aim to estimate a continuous variable based on the desired summary statistic instead of target loss.
These two types of problems have been historically studied with different mathematical tools because of these differences; however, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings.

@@

An important caveat to the above definitions is that, since $\Gamma = \prop{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\raf{Check me!}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

Since indirect elicitation is implied by both consistency and calibration of a surrogate $L \in \L$, it might seem a very weak necessary condition for consistency.
Yet, as we show in the following sections, it gives state-of-the-art lower bounds on the prediction dimension of consistent convex surrogates.
In particular, our bounds imply those given via feasible subspace dimension (Corollary~\ref{cor:fsd-bound}).\jessie{I might suggest cutting this paragraph for the sake of space?}
\raf{Kept it and squoze elsewhere}

@@

If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the regret with respect to $\ell$, the two definitions are equivalent. % for the appropriate choice of $\propdis$.
% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Given a surrogate loss $L$, link $\psi$, and target loss $\ell$, set
	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
  $\mu(r,p) := R_\ell(r,p)$.
  Then
	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
  \btw{Note: don't actually need $\gamma$ nonempty here.}
\end{lemma}
\jessie{Defer proofs to appendix from this section}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
        \begin{align}
	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf\nolimits_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
	\end{align}
        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
\end{proof}

@@

We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$.
\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.

### 2020-12-08 colt-21/infinite-outcomes.tex
Adding COLT 2021 files

\section{The OG proof, with our assumptions}
Consider the integral $I_f(u) = \int f(u,y) d(py)$ given the finite $\sigma$-algebra $(\Y, \A, p)$.

@@

Their proof goes as follows:
First, $\E_p \partial f(u,Y) \subseteq \partial F(u)$ for all $u \in \reals^d$ follows immediately \jessie{according to them... I don't see why} from the definition \jessie{of integration}, which implies the inclusion $\E_p \partial f(u,Y) + \Lambda(u) \subseteq \partial F(u)$ since $\vec 0 \in \Lambda(u)$.

Therefore, it is just left to prove $\partial F(u) \subseteq \E_p \partial f(u,Y) + \Lambda(u)$.

The proof proceeds by contradiction; if $\partial F(u) \neq \emptyset$ we can assume there is a $y_0 \in \partial F(u)$ so that $y_0 \not \in \E_p \partial f(u,Y) + \Lambda(u) = \E_p \partial f(u,Y)$.
Therefore, by some of their Lemmas~\cite[Lemmas 1, 2]{ioffe1969minimization}, we have $\E_p \partial f(u,Y)$ is not empty, convex, and closed, and can therefore be strictly separated from $y_0$.
Therefore, for some $z'$, we have $\langle z', y_0 \rangle \geq \langle z', y \rangle + \epsilon$ for some $\epsilon > 0$ and $y \in \E_p \partial f(u,Y)$

@@

Moreover, $\dom \psi = \reals$, and we have $\psi(z') \leq \langle z', y_0 \rangle - \epsilon$.
However, according to their Lemma 1, there exists a $y \in \E_p \partial f(u,Y)$ so that $\langle z', y \rangle = F'(u,z') = \langle z', y \rangle \leq \psi(z') < \langle z', y_0 \rangle$.\footnote{$F'(u,z')$ is the directional derivative of $F$ at $u$ in the $z'$ direction.}

>>>>

\section{The OG proof, with our assumptions}
Consider the integral $F(u) = \int f(u,y) d(py)$ given the finite $\sigma$-algebra $(\Y, \A, p)$.\footnote{Their notation: $F(u) = I_f(u)$.}

@@

Their proof goes as follows:
First, $\E_p \partial f(u,Y) \subseteq \partial F(u)$ for all $u \in \reals^d$ follows immediately \jessie{according to them... I don't see why} from the definition \jessie{of integration}.%, which implies the inclusion $\E_p \partial f(u,Y) + \Lambda(u) \subseteq \partial F(u)$. since $\vec 0 \in \Lambda(u)$.

Therefore, it is just left to prove $\partial F(u) \subseteq \E_p \partial f(u,Y)$.% + \Lambda(u)$.

The proof proceeds by contradiction; if $\partial F(u) \neq \emptyset$ we can assume there is a $y_0 \in \partial F(u)$ so that $y_0 \not \in \E_p \partial f(u,Y)$.% + \Lambda(u) = \E_p \partial f(u,Y)$.
Therefore, by some of their Lemmas~\cite[Lemmas 1, 2]{ioffe1969minimization}, we have $\E_p \partial f(u,Y)$ is not empty, convex, and closed, and can therefore be strictly separated from $y_0$.
Therefore, for some $z'$, we have $\langle z', y_0 \rangle \geq \langle z', y \rangle + \epsilon$ for some $\epsilon > 0$ and all $y \in \E_p \partial f(u,Y)$

@@

Moreover, $\effdom (\psi) = \reals^d$ by our assumptions (as $\E_p f(u,Y)$ is finite for all $u$), and we have $\psi(z') \leq \langle z', y_0 \rangle - \epsilon$.
However, according to their Lemma 1, there exists a $y \in \E_p \partial f(u,Y)$ so that $F'(u,z') = \langle z', y \rangle \leq \psi(z') < \langle z', y_0 \rangle$.\footnote{$F'(u,z')$ is the directional derivative of $F$ at $u$ in the $z'$ direction.}
